---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Cancan Jin"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()

#Mycode
ggplot(
  data = covid_data_count,
  mapping = aes(x = date, y = Cases, color = state)) +
  geom_point()
```

1. Write code for a plot and describe what you observe?

ggplot(
  data = covid_data_count,
  mapping = aes(x = date, y = Cases, color = state)) +
  geom_point()
  
I noticed that the number of deaths is largest in the state NV from 2021.04 to 2022.01. Also, the number of deaths doubled for most of the states from July to January.

2. Are there any conclusions you can draw?

The number of death grows rapidly from April to July and from October to January.

3. What were you not able to do due to not having the R knowledge?

I want to set up a simulated model for the data to estimate the cases of death in the future.

4. What other data would be useful to better understand this data?

I think "covid_data_count" would be more useful to understand the data. In the data set, the cases of different races are specified, which could better demonstrate the data.